### 2022-06-28 supplemental/OJEMB Supplementary Material.tex
Add to supplemental info

@@

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

@@

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

@@

\twocolumn[
\begin{@twocolumnfalse}
\thispagestyle{fancy}   
\vspace*{0.5cm}
\textbf{\LARGE{Supplementary Materials}}\\
\\
\medskip\Large{Title of the Manuscript}\\
\normalsize{ First A. Author,~\IEEEmembership{Fellow, IEEE,}
	Second B. Author,and Third C. Author*, Jr.,~\IEEEmembership{Member,~IEEE}}\\
	\vspace*{0.5cm}
\end{@twocolumnfalse}
]

@@

\IEEEPARstart{T}{he}  Supplementary Materials should either be organized in sections as per the main manuscript body (using up to 4,000 words) or it should be used to provide readers with a set of up to 10 additional display items (i.e. figures and tables).
Figures and tables should be prepared using the same format and guidelines as per the main body of the manuscript. References should be included using the same format utilized in the main body of the manuscript.

>>>>

\usepackage{soul}
\newcommand{\etal}{\textit{et al}., }
\newcommand{\ie}{\textit{i}.\textit{e}., }
\newcommand{\eg}{\textit{e}.\textit{g}.\ }
\newcommand{\cf}{\textit{cf}.\ }
\usepackage{hyperref}

@@

% *** MATH PACKAGES ***
%
\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

@@

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

@@

\twocolumn[
\begin{@twocolumnfalse}
\thispagestyle{fancy}   
\vspace*{0.5cm}
\textbf{\LARGE{Supplementary Materials}}\\
\\
\medskip\Large{Compressed Sensing for Characterization of Tinnitus}\\
\normalsize{ Alec Hoyland,
	Nelson Barnett, Benjamin W. Roop, Adam C. Lammert}\\
	\vspace*{0.5cm}
\end{@twocolumnfalse}
]

@@

\IEEEPARstart{T}his document contains a description of additional experiments to find a performant
stimulus generation method and a discussion of sparsity in tinnitus signals.
The code for all experiments is freely available at \url{https://github.com/alec-hoyland/tinnitus-project}
and the data are available upon request.

\section{Stimulus Generation}

In the context of this paper, a stimulus generation method
is a process that generates a random waveform that is:

\begin{enumerate}
  \item auditorally-distinguishable
  \item statistically uncorrelated, and
  \item similar to tinnitus percepts.
\end{enumerate}

Additionally, compressed sensing requires that the matrix of stimuli
should satisfy the restricted isometry property,
which many random matrices do with high probability (\eg Gaussian random matrices)
\cite{candesRestrictedIsometryProperty2008,candesIntroductionCompressiveSampling2008}.

\subsection{Auditorally-Distinguishable Stimuli}

We used mel-frequency binning to ensure that our stimuli were auditorally-distinguishable.
The mel scale is a perceptual scale of pitches judged by listeners to be equal in distance
from one to another (Fig. \ref{fig:hz2mel}) \cite{hamiltonTopographySpeechrelatedAcoustic2020}.

The formula

\begin{equation}
  m = 2595 \log_10 \bigg( 1 + \frac{f}{700} \big)
\end{equation}

converts $f$ Hz to $m$ mels.

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{gfx/hz2mel.eps}
	\caption{The relationship between Hz and mels is logarithmic.}
	\label{fig:hz2mel}
\end{figure}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,../paper/mybib}
